### 2015-11-16 ch02-qlogms/excitation-design.tex
Remove quite some duplicae sections

\subsection{Generic excitation signals}
\label{sec:excitation:intro:generic}
%TODO

\subsection{Optimal excitation signals}
\label{sec:excitation:intro:optimal}
Since generic excitation signals are not specifically geared towards the particular system under test, such signals tend to waste signal power.

%TODO

, such signals essentially don't use all the available signal power to reduce the uncertainty in the estimate.

@@

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
    Grid & Linear & Logarithmic & Quasi-logarithmic \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbers$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\leq \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\leq \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}
  \TODO{tabel: verschillende signalen: power per BW}

@@

\begin{figure}%
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{5cm}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz}.}%
  \label{fig:sumSys}
\end{figure}

>>>>

\subsection{Generic excitation signals}
\label{sec:excitation:intro:generic}
\TODO{\ldots}

\subsection{Optimal excitation signals}
\label{sec:excitation:intro:optimal}
Since generic excitation signals are not specifically geared towards the particular system under test, such signals use signal power in an inefficient way that does not reduce the variance of the model estimate significantly.
\TODO{\ldots}

@@

  \begin{table}
  \centering
   \caption{Summary of  properties of the different frequency grids.}
    \begin{tabular}{rccc} 
    \toprule
    Grid & Linear & Logarithmic & Quasi-logarithmic \\
    \midrule
    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Properties 
       & $f_0, \Delta f$ 
       & $f_0, \alpha$ 
       & $f_0, \Delta f, \alpha$\\
    \midrule
    $f_{k+1} \isdef$ 
       & $f_{k} + \Delta f$ 
       & $\alpha f_{k}$
       & $\round{\frac{\alpha^{N_k} f_k}{\Delta f}} \Delta f$,   $N_k \in \NaturalNumbers$
       \\[5pt]
    $\Delta f_k \isdef f_{k+1} - f_k$ 
       & $\Delta f$
       & $(\alpha - 1) f_k$
       & $ \in \NaturalNumbersWithoutZero \Delta f$ \\[5pt]
    $\alpha_k \isdef \frac{f_{k+1}}{f_k}$ 
       & $1 + \frac{\Delta f}{f_k}$ 
       & $\alpha$ 
       & $\approx \alpha $ \\[5pt]
    $F_{\ClosedInterval{a,b}}$
       & $\floor{\frac{b - a}{\Delta f}}$
       & $\floor{\log_{\alpha} \frac{b}{a}}$
       & $\leq \floor{\log_{\alpha} \frac{b}{a}}$\\[5pt]
    $F_{\ClosedInterval{f, \kappa f}}$
      & $\floor{\frac{(\kappa - 1)f}{\Delta f}}$
      & $\floor{\log_{\alpha} \kappa}$
      & $\leq \floor{\log_{\alpha} \kappa}$\\[5pt]
    \bottomrule
    \end{tabular}
  \end{table}

@@

\begin{figure}%
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{5cm}
  \input{\thisDir/figs/Sum02log0-2.tikz}
  \caption{FRF for the sum of two second order systems with $\damping=0.2$ and
           resonances at $ 400 \unit{Hz}$ and 4 \unit{kHz}.}%
           \TODO{also with other excitation signals?}
  \label{fig:sumSys}
\end{figure}

### 2015-11-16 ch02-qlogms/sysid.tex
Remove quite some duplicae sections

\section{Simulations}\label{sec:sim}
We considered a linear second order system that is to be identified, with the
only prior knowledge that its resonance frequency $\fR$ lies in a known
frequency band that may span several decades. 
Our goal is to identify such a system by means of a single excitation signal, 
such that the frequency response function (FRF) of the second order systems that are
equally damped are identified with the same uncertainty near their resonance.

\subsection{Excitation}
To excite the system under test, we used quasi-logarithmic (quasi-log) random-phase multisines. 
Their phase spectrum $\psi_{k}$ is the result of a uniform random process over $[0,2\pi[$.
A logarithmic spacing of the frequency components causes each decade within the band of interest to contain the same number of frequency components.

The quasi-log multisines were sampled at $f_s = 65\,536 \unit{Hz}$
and consisted of $N= 65\,536$ points such that the frequency spacing was $f_0 = 1\unit{Hz}$ for the linear grid.
This allowed the signal to cover four decades in the frequency domain,
from which we did not use the first decade.
Only frequencies between $1\unit{Hz}$ and $16\,384\unit{Hz}$ are excited, such that aliasing was avoided.

For the quasi-log excitation, a frequency ratio of $\alpha = 1.05$ was chosen
and the amplitude spectrum was kept constant $A_k = A_{\mathrm{in}}$. This
amplitude was normalized such that the root mean square (RMS) value of $u[n]$
was equal to $1$.

The desired frequency ratio $\alpha$ may not be attainable for low frequencies,  due to a lack of frequency resolution.
This causes a less dense coverage of the lowest frequency bands.

\subsection{System under test}
The systems we studied are low-pass second order systems with a given damping
$\damping$, resonance frequency $\fR$ and a DC gain of $0 \unit{dB}$. Such systems
can be represented in the discrete frequency domain by a transfer
function of the form:
\begin{equation}
  G \left( z \right) = \frac{         b_2  z^{2} + b_1 z + b_0}%
                            {\phantom{a_2} z^{2} + a_1 z + a_0}
  \text{.}
  \label{eq:tf}
\end{equation}

These discrete-time systems were constructed using the \matlab\ function \texttt{cheby1}.

An output error (OE) model was used to describe the system under test with the
input $u[n]$, the system output $y_0[n]$, the white noise source $e[n]$
and the measured output $y[n] = y_0[n] + e[n]$.

\subsection{Simulation setup}
First, we considered a system with damping $\damping=0.05$ and resonant
frequency $\fR = 40 \unit{Hz}$.

The output noise $e[n]$ was white Gaussian noise with a standard deviation
$\sigma_e = 0.1123$ which was approximately $10$ times smaller than the
root mean square (RMS) value $y_0[n]$.

The simulations were repeated $R=1000$ times for each system with different realizations of the multisines $u[n]$ and the noise $e[n]$.
In order to avoid that all simulations started with zero initial conditions, $N + N_{\mathrm{trans}}$ data points were generated, from which the first $N_{\mathrm{trans}}$ points of each simulation were discarded.

\subsection{Results for a single system}
The outcome of the simulation over these repetitions are displayed in \figref{fig:FRF1}.
These results show the averaged estimated FRF ($\hat{G}$), the standard deviation  $\sigma_{\hat{G}}$ on these estimates, the true FRF ($G_0$) and the bias of the estimates ($\Bias (\hat{G})$).

These graphs show that the bias is more than $20 \unit{dB}$ less than the variance.
This means that the mean square error (MSE) of the estimated FRFs is mainly caused by the variance $\sigma_{\hat{G}}^2$ and not by a large bias.

\begin{figure}[hpt]
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{5cm}
  \input{\thisDir/figs/Sys005log0-1.tikz}
  \caption{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.05$ 
           along with its variance and bias.}%
           \TODO{reproduce figure with ALL excitation signals}
  \label{fig:FRF1}
\end{figure}

\subsection{Simulations on a range of second order systems}
The simulation carried out above was repeated for a more general set of systems.
We studied systems with both a damping of $\damping=0.05$ (as above) and $\damping=0.2$.
For these different damping values, systems with resonant frequencies
$\fR \in \{ 40  \unit{Hz}\!,$
          $ 80  \unit{Hz}\!,$
          $200  \unit{Hz}\!,$
          $400  \unit{Hz}\!,$
          $800  \unit{Hz}\!,$
          $  2 \unit{kHz}\!,$
          $  4 \unit{kHz}\!\}$ were considered.
The parameters pertaining to sampling and the excitation signal were left unchanged
from the previous simulations. For the systems with a damping of $0.2$, $\sigma_e$
was put at $0.0678$, which is approximately $10\%$ of the RMS value of $y_0[n]$.
To allow an easy comparison with a multisine with an equidistant (linear) frequency grid, we also evaluated the variance for such an excitation signal (which had all other parameters determined similarly to the quasi-log multisines).

In \figref{fig:damping005} and \figref{fig:damping02} the results from these
simulations are presented in a condensed form. 
They show the mean estimated FRFs ($\hat{G}$), the true FRFs ($G_0$) and the corresponding standard deviations ($\sigma_{\hat{G}}$) near the resonance frequency of the simulated systems.
The bias was at least $20\unit{dB}$ smaller than the standard deviation as well, but is omitted from the figures for clarity.

We can verify that for the smaller damping ($\damping=0.05$ in \figref{fig:damping005})
the variance near the resonance is almost identical for all systems at $-39.3\unit{dB} \pm 1.8 \unit{dB}$.

For the systems that are damped more ($\damping=0.2$ in \figref{fig:damping02}),
we observe that the variance is nearly constant over the frequency range as well.
The standard deviation lies at around $-49.3 \unit{dB} \pm 2.2\unit{dB}$.
Systems that have a lower resonance frequency, exhibit a slightly higher variance 
on their estimated FRF (near the resonance).

The logarithmically-spaced excitation provides a much more constant dependency of resonance frequency to the variance than a linearly-spaced multisine, where the variance varies over respectively $35$ and $25 \unit{dB}$.

\begin{figure}%
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{5cm}
  \input{\thisDir/figs/damping005-cmp.tikz}
  \caption{Comparison of the FRF and corresponding variances for
           different second order systems with constant damping
           $\damping=0.05$ but different resonance frequencies around
           their respective resonance frequencies, for both a quasi-log 
           and a linear multisine excitation.}%
  \label{fig:damping005}
\end{figure}

\begin{figure}%
  \centering
  \setlength{\figurewidth}{0.8\columnwidth}
  \setlength{\figureheight}{5cm}
  \input{\thisDir/figs/damping02-cmp.tikz}
  \caption{Comparison of the FRF and corresponding variances for
           different second order systems with constant damping
           $\damping=0.2$ but different resonance frequencies around
           their respective resonance frequencies, for both a quasi-log 
           and a linear multisine excitation.}%
  \label{fig:damping02}
\end{figure}

\subsection{Conclusion}
The variance on the FRF near resonances with identical damping is nearly independent of the resonance frequency when a quasi-log multisine is used as excitation signal. 
This result was obtained for second order sections and illustrated on a more general system.

>>>>

% \section{Simulations}\label{sec:sim}
% We considered a linear second order system that is to be identified, with the
% only prior knowledge that its resonance frequency $\fR$ lies in a known
% frequency band that may span several decades. 
% Our goal is to identify such a system by means of a single excitation signal, 
% such that the frequency response function (FRF) of the second order systems that are
% equally damped are identified with the same uncertainty near their resonance.

% \subsection{Excitation}
% To excite the system under test, we used quasi-logarithmic (quasi-log) random-phase multisines. 
% Their phase spectrum $\psi_{k}$ is the result of a uniform random process over $[0,2\pi[$.
% A logarithmic spacing of the frequency components causes each decade within the band of interest to contain the same number of frequency components.

% The quasi-log multisines were sampled at $f_s = 65\,536 \unit{Hz}$
% and consisted of $N= 65\,536$ points such that the frequency spacing was $f_0 = 1\unit{Hz}$ for the linear grid.
% This allowed the signal to cover four decades in the frequency domain,
% from which we did not use the first decade.
% Only frequencies between $1\unit{Hz}$ and $16\,384\unit{Hz}$ are excited, such that aliasing was avoided.

% For the quasi-log excitation, a frequency ratio of $\alpha = 1.05$ was chosen
% and the amplitude spectrum was kept constant $A_k = A_{\mathrm{in}}$. This
% amplitude was normalized such that the root mean square (RMS) value of $u[n]$
% was equal to $1$.

% The desired frequency ratio $\alpha$ may not be attainable for low frequencies,  due to a lack of frequency resolution.
% This causes a less dense coverage of the lowest frequency bands.

% \subsection{System under test}
% The systems we studied are low-pass second order systems with a given damping
% $\damping$, resonance frequency $\fR$ and a DC gain of $0 \unit{dB}$. Such systems
% can be represented in the discrete frequency domain by a transfer
% function of the form:
% \begin{equation}
%   G \left( z \right) = \frac{         b_2  z^{2} + b_1 z + b_0}%
%                             {\phantom{a_2} z^{2} + a_1 z + a_0}
%   \text{.}
%   \label{eq:tf}
% \end{equation}

% These discrete-time systems were constructed using the \matlab\ function \texttt{cheby1}.

% An output error (OE) model was used to describe the system under test with the
% input $u[n]$, the system output $y_0[n]$, the white noise source $e[n]$
% and the measured output $y[n] = y_0[n] + e[n]$.

% \subsection{Simulation setup}
% First, we considered a system with damping $\damping=0.05$ and resonant
% frequency $\fR = 40 \unit{Hz}$.

% The output noise $e[n]$ was white Gaussian noise with a standard deviation
% $\sigma_e = 0.1123$ which was approximately $10$ times smaller than the
% root mean square (RMS) value $y_0[n]$.

% The simulations were repeated $R=1000$ times for each system with different realizations of the multisines $u[n]$ and the noise $e[n]$.
% In order to avoid that all simulations started with zero initial conditions, $N + N_{\mathrm{trans}}$ data points were generated, from which the first $N_{\mathrm{trans}}$ points of each simulation were discarded.

% \subsection{Results for a single system}
% The outcome of the simulation over these repetitions are displayed in \figref{fig:FRF1}.
% These results show the averaged estimated FRF ($\hat{G}$), the standard deviation  $\sigma_{\hat{G}}$ on these estimates, the true FRF ($G_0$) and the bias of the estimates ($\Bias (\hat{G})$).

% These graphs show that the bias is more than $20 \unit{dB}$ less than the variance.
% This means that the mean square error (MSE) of the estimated FRFs is mainly caused by the variance $\sigma_{\hat{G}}^2$ and not by a large bias.

% \begin{figure}[hpt]
%   \centering
%   \setlength{\figurewidth}{0.8\columnwidth}
%   \setlength{\figureheight}{5cm}
%   \input{\thisDir/figs/Sys005log0-1.tikz}
%   \caption{FRF of a second order system with $\fR=40\unit{Hz}$ and $\damping=0.05$ 
%            along with its variance and bias.}%
%            \TODO{reproduce figure with ALL excitation signals}
%   \label{fig:FRF1}
% \end{figure}

% \subsection{Simulations on a range of second order systems}
% The simulation carried out above was repeated for a more general set of systems.
% We studied systems with both a damping of $\damping=0.05$ (as above) and $\damping=0.2$.
% For these different damping values, systems with resonant frequencies
% $\fR \in \{ 40  \unit{Hz}\!,$
%           $ 80  \unit{Hz}\!,$
%           $200  \unit{Hz}\!,$
%           $400  \unit{Hz}\!,$
%           $800  \unit{Hz}\!,$
%           $  2 \unit{kHz}\!,$
%           $  4 \unit{kHz}\!\}$ were considered.
% The parameters pertaining to sampling and the excitation signal were left unchanged
% from the previous simulations. For the systems with a damping of $0.2$, $\sigma_e$
% was put at $0.0678$, which is approximately $10\%$ of the RMS value of $y_0[n]$.
% To allow an easy comparison with a multisine with an equidistant (linear) frequency grid, we also evaluated the variance for such an excitation signal (which had all other parameters determined similarly to the quasi-log multisines).

% In \figref{fig:damping005} and \figref{fig:damping02} the results from these
% simulations are presented in a condensed form. 
% They show the mean estimated FRFs ($\hat{G}$), the true FRFs ($G_0$) and the corresponding standard deviations ($\sigma_{\hat{G}}$) near the resonance frequency of the simulated systems.
% The bias was at least $20\unit{dB}$ smaller than the standard deviation as well, but is omitted from the figures for clarity.

% We can verify that for the smaller damping ($\damping=0.05$ in \figref{fig:damping005})
% the variance near the resonance is almost identical for all systems at $-39.3\unit{dB} \pm 1.8 \unit{dB}$.

% For the systems that are damped more ($\damping=0.2$ in \figref{fig:damping02}),
% we observe that the variance is nearly constant over the frequency range as well.
% The standard deviation lies at around $-49.3 \unit{dB} \pm 2.2\unit{dB}$.
% Systems that have a lower resonance frequency, exhibit a slightly higher variance 
% on their estimated FRF (near the resonance).

% The logarithmically-spaced excitation provides a much more constant dependency of resonance frequency to the variance than a linearly-spaced multisine, where the variance varies over respectively $35$ and $25 \unit{dB}$.

% \begin{figure}%
%   \centering
%   \setlength{\figurewidth}{0.8\columnwidth}
%   \setlength{\figureheight}{5cm}
%   \input{\thisDir/figs/damping005-cmp.tikz}
%   \caption{Comparison of the FRF and corresponding variances for
%            different second order systems with constant damping
%            $\damping=0.05$ but different resonance frequencies around
%            their respective resonance frequencies, for both a quasi-log 
%            and a linear multisine excitation.}%
%   \label{fig:damping005}
% \end{figure}

% \begin{figure}%
%   \centering
%   \setlength{\figurewidth}{0.8\columnwidth}
%   \setlength{\figureheight}{5cm}
%   \input{\thisDir/figs/damping02-cmp.tikz}
%   \caption{Comparison of the FRF and corresponding variances for
%            different second order systems with constant damping
%            $\damping=0.2$ but different resonance frequencies around
%            their respective resonance frequencies, for both a quasi-log 
%            and a linear multisine excitation.}%
%   \label{fig:damping02}
% \end{figure}

% \subsection{Conclusion}
% The variance on the FRF near resonances with identical damping is nearly independent of the resonance frequency when a quasi-log multisine is used as excitation signal. 
% This result was obtained for second order sections and illustrated on a more general system.
